A Sound Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2022-06-20 paper/paper.tex
Fixing a typo

In this work, we presented a sound deep embedding of arbitrary
normal modal logics in Coq. Our approach is able to represent uniformly
deduction over different modal logic systems by using different axiom sets
as predicate parameter in the deduction inductive type. Using this generic
representation of deduction we are able to prove the soundness theorem and
apply it on proving L\"ob's theorem.

>>>>

In this work, we presented a sound deep embedding of arbitrary
normal modal logics in Coq. Our approach is able to represent uniformly
deduction over different modal logic systems by using different axiom sets
as a predicate parameter in the deduction inductive type. Using this generic
representation of deduction we are able to prove the soundness theorem and
apply it on proving L\"ob's theorem.
